Measurement of a dwarf galaxy rotational velocity from its Lyman-alpha line emission

### 2016-08-08 paper/letter.tex
rewriting physical interpretation

\section*{MCMC constraints}

@@

There is an upper limit for the  
integrated flux of $<0.10$ Jy km s$^{-1}$, which translates into a
upper limit for the HI mass of $M<2.65\times 10^{8}$ M$_{\odot}$
\cite{pustilnikmartin07}. 
From the optical depth of $10^7$ and the non-detection in the HI line,
we have an upper limit for the size where the Lya emission comes of
$D<0.34$kpc.

@@

The first important effect of rotation is that it breaks the spherical
symmetry of the static case. 
Now the line's observed morphology depends on the angle between the
line-of-sight (LOS) and the rotation axis. 
LOS parallel to the rotation axis tend to observed the line without
any modification from rotation, while the perpendicular LOS will
observe a maximal change in the line's morphology due to rotation.

There is a concise analytical description for those features.
This description takes into account how different parts of the
sphere's surface shift in frequency the \lya photons. 
Different shifts in frequency come from different values for the projected
velocity along the LOS. 
As presented in \cite{CLARA}, using the analytical solution for the
\lya sphectra of a static sphere plus the right frequency shifts
computed from geometrical considerations, one is able to produce an
analytical solution for the rotating sphere that reproduces the main
features found with the full numerical simulation.

\section*{The Multiphase Model}
The idealized multiphase model consists of spherical, cold, dens
clumps of neutral hydrogen (and dust) embedded in a hot, ionized
medium. The clumps also have a random and an outflowing velocity
component which totals the number of parameters describing the model
to be $14$. In order to map out this large parameter space, we
randomly drew $2500$ sets of parameters within a observationally
realistic range (based on the considerations of
\cite{Laursen2013ApJ...766..124L}) yielding a large variety of
single-, double- and triple-peaked spectra. The full analysis of the
the spectral features as well as more details on the radiative
transfer are presented in \cite{Gronke2016}.

\textbf{MG: I don't know how much details you want -- should we name
  all of the $14$ (best fit) parameters? Just delete what is
  unnecessary.}

For the current work, we computed the $\chi^2$ for each of the $2500$
parameters yielding the best fit parameters of $(...)$. Here, the
subscripts ${}_{\rm cl}$ and $_{\rm ICM}$ stand for the quantities
filling the clumps and the medium between the clumps,
respectively. Furthermore, we found that some parameters such as the
magnitude of the random clump motion $\sigma_{\rm cl}$ improved the
fit significantly whereas others did not. This makes sense also
qualitatively as \tol\ possesses a very wide spectrum which can be
achieved by subsequent scatterings off (relatively) fast moving clumps
while the multi-phase nature (i.e., the existence of low-density
channels) ensures the high flux at line center as observed.

>>>>

There is an upper limit for the  
integrated flux of $<0.10$ Jy km s$^{-1}$, which translates into a
upper limit for the HI mass of $M<2.65\times 10^{8}$ M$_{\odot}$
\cite{pustilnikmartin07}.

The first important effect of rotation is that it breaks the spherical
symmetry of the static case. 
Now the line's observed morphology depends on the angle $\theta$ between the
line-of-sight (LOS) and the rotation axis. 
LOS parallel to the rotation axis tend to observed the line without
any modification from rotation, while the perpendicular LOS will
observe a maximal change in the line's morphology due to rotation.

There is a concise analytical description for those features.
This description takes into account how different parts of the
sphere's surface shift in frequency the \lya photons. 
Different shifts in frequency come from different values for the projected
velocity along the LOS. 
As presented in \cite{CLARA}, using the analytical solution for the
\lya sphectra of a static sphere plus the right frequency shifts
computed from geometrical considerations, one is able to produce an
analytical solution for the rotating sphere that reproduces the main
features found using the full numerical simulation.

The analytical solution for the rotation sphere was the base to
perform the Markov Chain Monte Carlo Calculation using the
\texttt{emcee} implementation.
We explore flat priors on $V_{\rm max}$ $\log_{10}\tau$, $\log_{10} T$ and
$\theta$ using $XX$ steps.
The results are summarized in Figure $XX$. 
From this model we find that the fiducial parameters that could
explain the broad features in \tol\ are $V_{\rm max}$, $\log \tau
=XX$, $\log_{10} T = $ and  $\theta =$

\section*{The Multiphase Model}

The idealized multiphase model consists of spherical, cold, dens
clumps of neutral hydrogen (and dust) embedded in a hot, ionized
medium. 
The clumps also have a random and an outflowing velocity
component which totals the number of parameters describing the model
to be $14$. 
In order to map out this large parameter space, we randomly drew
$2500$ sets of parameters within a observationally realistic range
(based on the considerations of \cite{Laursen2013ApJ...766..124L})
yielding a large variety of single-, double- and triple-peaked
spectra. 
The full analysis of the the spectral features as well as
more details on the radiative transfer are presented in
\cite{Gronke2016}.

For the current work, we computed the $\chi^2$ for each of the $2500$
parameters yielding the best fit parameters of $(...)$. Here, the
subscripts ${}_{\rm cl}$ and ${}_{\rm ICM}$ stand for the quantities
filling the clumps and the medium between the clumps,
respectively. 
Furthermore, we found that some parameters such as the magnitude of
the random clump motion $\sigma_{\rm cl}$ improved the fit
significantly whereas others did not.

Qualitatively as \tol\ possesses a very wide spectrum which can be
achieved by subsequent scatterings off (relatively) fast moving clumps
while the multi-phase nature (i.e., the existence of low-density
channels) ensures the high flux at line center as observed.

@@

Both the rotation and the multiphase model constrain the typical
velocity of the HI gas, with and additional constrain on the typical
size for the emission region, $D$, on could estimate a dynamical mass with

\begin{equation}
M_{\rm dyn} = \frac{V^{2}D}{G} = 2.16\times10^{5}
\left(\frac{V}{\mathrm{km\ s}^{-1}}\right)^2\left(\frac{D}{\mathrm{kpc}}\right) M_{\odot}
\end{equation}

The multiphase model also sets a typical size for the region where the
clumps are confined.
In the rotation model the size of that region can be infered from the
constraint on the total HI mass.

From the optical depth of $10^7$ and the non-detection in the HI line,
we have an upper limit for the size where the Lya emission comes of
$D<0.34$kpc.

@@
